% !TeX root = resume
\cvsection{Extracurricular activities}
\begin{cventries}
  \cventry
    {Tutor and fundraising assistant}
    {Mu Nu Chapter of IEEE-Eta Kappa Nu}
    {Dec 2016 - present}
    {}
    {
      \begin{cvitems}
      	\item {Managed tutoring sessions for Electronic Engineering student.}
      	\item {Helped finding companies willing to fund the association or sponsor its events.}
        \item {IEEE-Eta Kappa Nu is the honor society of IEEE recognizing excellence among the students in the fields of electronic and computer engineering.}
        \item {This chapter at Politecnico is the first in Europe.}        
      \end{cvitems}
    }
    
  \cventry
    {Winter School}
    {Alta Scuola Politecnica}
    {Mar 2017}
    {}
    {
      \begin{cvitems}
        \item {Took part in the fourth school of the XII cycle of ASP, contributing to the teamwork.}
        \item {One week of seminars and group work based on "Complex decision making under emergency conditions".}
        \item {Learned techniques which help during the decision making process.}
      \end{cvitems}
    }
    
  \cventry
    {English course Level C1}
    {The Burlington School of English, London}
    {Aug 2013}
    {}
    {
      \begin{cvitems}
        \item {Summer school offered to a selected group of students from \emph{IIS 8 Marzo} high school.}
      \end{cvitems}
    }
    
  \cventry
    {English course Level B2}
    {Oakdale College, London}
    {Aug 2012}
    {}
    {
      \begin{cvitems}
        \item {Summer school offered to a selected group of students from \emph{IIS 8 Marzo} high school.}
      \end{cvitems}
    }
\end{cventries}

\pagebreak
